### 2015-07-06 narrative/evaluation.tex
significant readability improvements and hopefully additional clarity

In order to determine if our guiding principles are being met, and we can
optimize the system from these guiding principles, we will evaluate our work
using the Table~\ref{table:eval}.

To determine the effectiveness of the components of our proposed work we will
partition the problem along the lines of our two guiding principles. 
We will evaluate how the knowledge centric system design we employ can
provide a more predictable level of performance and data quality.

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{tabular}{ | l | l | l | }

  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric}                  & More knowledge = faster access  &  More knowledge = better \\
  {\bf system}                             & to higher quality data          &  resource utilization across \\
                                           &                                 & the entire hierarchy \\ \hline

  {\bf Predictable Performance} & More predictability =                     &  Accuracy of the time bounds \\
  {\bf Accuracy}                & better quality of data                    &  across multiple layers of the\\
                                           &                                           &  storage hierarchy wrote/read \\ 
                                           &                                           &  in time constrained\\
                                           &                                           &  situations \\ \hline

\end{tabular}

In addition to benchmarking the various S2E2 methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp),
PPPL (C. S. Chang), and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate the leading edge applications along with the system performance.
We will use the systems at both SNL and OLCF, which have multiple layers of
storage. For example, the sith cluster at the OLCF
(https://www.olcf.ornl.gov/computing-resources/sith/) has its own Lustre
storage system, SSDs on each node, and is connected to the center-wide Lustre
file system. We will perform testing in both the system level (on sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.

Our evaluation will include how accurately we can set the bounds on
time estimates for applications. We will measure these estimates when data
is on just one level of the storage hierarchy, as well as
accesses that include data chunks on multiple levels.
We will evaluate how fast data can be discovered
when it is split between levels, allowing us to better understand how
finely data can be split before it takes too long to access.
We will also evaluate our techniques to examine how well we can
migrate data and update our server to determine if data might get
out-of-sync between data chunks. We will need to clearly understand how well
this system works on current systems and we will need to investigate this on
the next generation OLCF system such as Summit, to which we will have early access.

Another area of investigation will be in how accurately data can be read 
when there are time constraints due to users wanting to read in many time
slices in a given amount of time. For example, in J. Tromp's visualization,
we may be interested in looking at hundreds of time slices, but when we visualize this data we
would like very fast access to the ``first look'' of the data. The question
is whether the high priority data will be sufficiently representative of the overall data. Can
we make accurate visualization from the less accurate data? We will work
with our application partners to assess this, and we will determine the
accuracy in time-constrained test vs. test which will not place any bounds
on the time to retrieve the data.

We will also want to assess how well our data migration and eviction
policies work with user-knowledge. Will the overall system be able to
utilize more of the storage hierarchy by understanding these intentions and
creating autonomic rules to self-optimize? Furthermore we will want to see
if users can give us more accurate policies which can then be used for
better system resource utilization. If we have more knowledge we would like
to be able to show that this will translate into higher levels of
system utilization.

One of the risks we face in our design is the unwillingness of users to add
more knowledge to the system. To better understand the burden on the user we
will attempt to quantify the additional burden on the users in relation to
the additional knowledge required for optimization. 
 We realize that initially it will be a large burden for users to
place initial knowledge into the system, but we will evaluate the results as
users increase the knowledge placed into the system with the overall burden.
Our hypothesis from working with many LCF users is that once they get over
the initial burden of placing this knowledge the burden decreases as more
knowledge is placed into the system, and thus, they will be more inclined to
increase the knowledge into the system as the benefits increase.

We will also need to evaluate to what extent more knowledge about
the data will lead to increased performance achieved by placing the most important pieces at the
higher layers of the hierarchy. We will evaluate this by increasing and
decreasing this knowledge, and comparing the effects. For example, if the user doesn't want their data
broken into priority chunks, then the data will be at the mercy of what the
system does with no knowledge. If the user then gives us information that
allows us to use ``generic'' routines based on frequency, or accuracy, then
we can use that knowledge to decompose the objects into chunks which can be
placed. We can evaluate these questions by working with specific users who
are in a position give us more knowledge,
allowing us to perform application level binning of data (for example
for C.S. Chang), or for level of features (for J. Tromp).

>>>>

Our guiding principles are the basis for the evaluation. These principles are
described in Table~\ref{table:eval}.  We will partition the problem along these
lines and evaluate how the knowledge centric system design we employ can
provide more predictable performance and data quality.

%I dont think this table is right. Knowledge is our independent variable
%and predictability is our dependent variable
\begin{table}[ht]
\caption{Guiding Principles}
\label{table:eval}
\centering
\begin{tabular}{ | p{1.4in} | p{2in} | p{2in} | }
  \hline
  {\bf Principle/Metric}                   & {\bf User perspective metric}   & {\bf System perspective metric }\\ \hline
  {\bf Knowledge-centric system}           & More knowledge = faster access to higher quality data &  More knowledge = better resource utilization across the entire hierarchy \\ \hline
  {\bf Predictable Performance Accuracy}   & More predictability = better quality of data &  Accuracy of the time bounds across multiple layers of the storage hierarchy wrote/read in time constrained situations\\ \hline
\end{tabular}
\end{table}

In addition to benchmarking the various S2E2 methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp),
PPPL (C. S. Chang), and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate the leading edge applications working with the storage system to
determine performance predictability and data quality.  Our evaluation will
will use the multiple storage layers available on systems at both SNL and the
OLCF.  For example, the sith cluster at the OLCF
(https://www.olcf.ornl.gov/computing-resources/sith/) has its own Lustre
storage system, SSDs on each node, and is connected to the center-wide Lustre
file system. We will perform test in both the system level (on sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.

The first part of our evaluation will cover the following characteristics: (1)
the accuracy of time bounds estimates for applications when data is on just one
level of the storage hierarchy as well as when the data chunks are split; (2)
data discovery speed when chunks are spread across the hierarchy informing how
many pieces data can be split into before it takes too long to access most of
the data; and (3) how well we can migrate data and update our server to
determine if data might get out-of-sync between data chunks.  We will need to
clearly understand how well this system works on current systems and we will
need to investigate this on the next generation OLCF system (Summitt) and the
SNL system (Trinity) which we will have early access, along with all of the
applications we will be investigating.

The second part of our evaluation will cover data accuracy for data read when
there are time constraints due to users wanting to read in many time slices in
a given amount of time. For example, J. Tromp's visualization may contain
hundreds of time slices, but when we visualize this data, we would like very
fast access to the data ``first look''. We will determine if the data will be
sufficiently representative of the overall data.  We will work with our
application partners to assess the visualization accuracy using different data
qualities including comparisons between a time-constrained test vs. a test
without any time constraints for data retrieval.

The third part of the evaluation will assess how well our data migration and
eviction policies work with user-knowledge. We will determine if the overall
system is able to use more of the storage hierarchy by understanding these
intentions and creating autonomic rules to self-optimize. Furthermore, we will
determine if users can give more accurate policies that lead to better system
resource utilization. We specifically will evaluate if more knowledge
translates into higher levels of system utilization.

The fourth part of the evaluation focuses on the additional user burden. One of
the risks in the proposed design is the unwillingness of users to add more
knowledge to the system. To better understand the user burden, we will attempt
to quantify the additional requirements to improve the automatic optimization.
We expect a substantial minimal burden to inform the automatic optimization.
Our evaluation will focus on the improvements gained through additional user
provided data and attempt to relate the pain/benefit tradeoff. The initial
hypothesis from working with many LCF users suggests that once the initial
burden to facilitate the automatic optimization, the additional burden required
to increase benefits is small enough to encourage users to participate more
heavily for greater benefit.

The fifth part of the evalation will evaluate how well additional data
knowledge in the system will lead to more performance by placing the most
important pieces at the higher layers of the hierarchy. We will test different
knowledge levels and evaluate the system impact.  For example, if the user
doesn't want the data broken into priority chunks, then the data will be at
the mercy of what the system does when there is no knowledge. If the user then 
provides sufficient information to use ``generic'' rouitnes based on frequency
or accuracy, then that knowledge will be used to decompose the objects into
specially placed chunks. We will evaluate these no and minimal knowledge cases
against those that provide additional knowledge allowing application level data
binning (for C.S. Chang) or for level of features (for J. Tromp).
